Understanding the problem of when to scale

### 2024-04-23 presentations/understanding the problem.qmd
print wd
selv contained

---
title: "Understanding the problem of when to scale"
format: 
  revealjs:
    smaller: true
    scrollable: false
    preview-links: true
editor: visual
---

@@

------------------------------------------------------------------------
## Commutativty

>>>>

---
title: "Understanding the problem of when to scale"
format: 
  revealjs:
    smaller: true
    scrollable: false
    preview-links: true
    self-contained: true
editor: visual
---

@@

## Commutativty
